Ice sheet mass flows

### 2024-06-24 sankey.tex
Adjust frontal advance

    \sankeyset{
      %% comment for gray outline
      draw/.style={
        draw=white,
        line width=0pt,line cap=round,line join=round,
      },
      every node/.style={angle=-90},
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/33,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      ice-to-water/.style={fill/.style={fill=none, top color=ice, bottom color=water},},
      ice-to-water-horiz/.style={fill/.style={fill=none, right color=ice, left color=water},},
      ice-to-air/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-air-horiz/.style={fill/.style={fill=none, left color=ice, right color=air},},
      water-to-air-horiz/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, top color=water, bottom color=air},},
      air-to-ice/.style={fill/.style={fill=none, top color=air, bottom color=ice},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      red-to-ice/.style={fill/.style={fill=none, top color=red, bottom color=ice},},
      water-to-ice/.style={fill/.style={fill=none, top color=water, bottom color=ice},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\ttfamily,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

    \ifthenelse{\Q{vMG} > \Q{vML}} {
      \ifthenelse{\Q{vFRLOSS} > 0}{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vRFZ}/RFZi}}
      }{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\Q{vFRGAIN}/FG, \qq{f0}/f0i, \Q{vRFZ}/RFZi}}
      }
    } {
      \ifthenelse{\Q{vFRLOSS} > 0}{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vML}/MLi, \Q{vRFZ}/RFZi}}
      }{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\Q{vFRGAIN}/FG, \qq{f0}/f0i, \Q{vML}/MLi, \Q{vRFZ}/RFZi}}
      }
    }

    \ifthenelse{\Q{vFRGAIN} > 0}{
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[yshift=15mm,xshift=\xoff]FG.left}, anchor=right}
      \sankeystart{FGi}
      \abovelabel{FGi}{Frontal advance}
      \sankeyoutin{FGi}{FG}
    }{}

>>>>

    \sankeyset{
      %% comment for gray outline
      draw/.style={
        draw=white,
        line width=0pt,line cap=round,line join=round,
      },
      every node/.style={angle=-90},
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/33,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      ice-to-water/.style={fill/.style={fill=none, top color=ice, bottom color=water},},
      ice-to-water-horiz/.style={fill/.style={fill=none, right color=ice, left color=water},},
      ice-to-air/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-air-horiz/.style={fill/.style={fill=none, left color=ice, right color=air},},
      water-to-air-horiz/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, top color=water, bottom color=air},},
      air-to-ice/.style={fill/.style={fill=none, top color=air, bottom color=ice},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      red-to-ice/.style={fill/.style={fill=none, top color=red, bottom color=ice},},
      water-to-ice/.style={fill/.style={fill=none, top color=water, bottom color=ice},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      black-to-ice/.style={fill/.style={fill=none, bottom color=ice, top color=black},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\ttfamily,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

    \ifthenelse{\Q{vMG} > \Q{vML}} {
      \ifthenelse{\Q{vFRLOSS} > 0}{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vRFZ}/RFZi}}
      }{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vFRGAIN}/FG, \Q{vRFZ}/RFZi}}
      }
    } {
      \ifthenelse{\Q{vFRLOSS} > 0}{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vML}/MLi, \Q{vRFZ}/RFZi}}
      }{
        \sankeynode{name=f1, quantity=\Q{vRFZ}+\qq{f0}+\Q{vML}+\Q{vFRGAIN},
          at={[yshift=-15mm]f0.left}, anchor=left,
          forked={\qq{f0}/f0i, \Q{vML}/MLi, \Q{vFRGAIN}/FG, \Q{vRFZ}/RFZi}}
      }
    }

    \ifthenelse{\Q{vFRGAIN} > 0}{
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[yshift=15mm,xshift=-\xoff]FG.right}, anchor=left}
      \sankeystart[black]{FGi}
      \sankeyoutin[black-to-ice]{FGi}{FG}
      \node[font=\tiny, rotate=45, anchor=north east]
      at ([yshift=12mm,xshift=3mm]FGi.right) {Frontal advance: \qq{FGi}}; 
   }{}
